Lonely and online: an investigation of social media use and social isolation in China

### 2023-10-08 tandf/Social Isolation in China.qmd
File cleanup

---
title: "Lonely and online: an investigation of social media use and social isolation in China"
date: '`r format(Sys.time(), "%B %d, %Y")`'
abstract: "Early research and popular discourse on the promise of the internet's impact on social isolation was optimistic. Since these early predictions, research has become less positive, usually pointing to the negative role of social media, withn more recent studies focused on heterogeneous effects. Using data from a nationwide survey of Chinese citizens to gain leverage on this disagreement in the literature, our research finds support for those that have focused on heterogeneous effects - we find that urbancity is a key moderating variable. Additionally, our results lend support to a FOMO mechanism while they are not suggestive of a mechanism by which negative content is the channel through which social media generates feelings of social isolations. Overall, our findings suggest that institutional context may not play an important role in the social media - social isolation relationship."
keywords: [Social Isolation, Social Media, Digital Communication, China]
format:
  tandf-pdf:
    keep-tex: true 
execute: 
  echo: false
  warning: false
keep-tex: true
bibliography: references.bib
csl: taylor-and-francis-apa.csl
author:
  - name: Jason Gainous
    affiliations:
      - name: University of Sharjah
        department: Department of Mass Communication
        city: Sharjah
        country: United Arab Emirates
    orcid: 0000-0002-3104-2313
    email: jgainous@sharjah.ac.ae
  - name: Andrew W. MacDonald
    affiliations:
      - name: Duke Kunshan University
        department: Division of Social Sciences
        city: Kunshan
        country: China
    orcid: 0000-0002-4695-1560
    email: andrew.macdonald@dukekunshan.edu.cn
    attributes:
      corresponding: true
---

>>>>

---
title: "Lonely and online: an investigation of social media use and social isolation in China"
date: '`r format(Sys.time(), "%B %d, %Y")`'
abstract: "Early research and popular discourse on the promise of the internet's impact on social isolation was optimistic. Since these early predictions, research has become less positive, usually pointing to the negative role of social media, withn more recent studies focused on heterogeneous effects. Using data from a nationwide survey of Chinese citizens to gain leverage on this disagreement in the literature, our research finds support for those that have focused on heterogeneous effects - we find that urbancity is a key moderating variable. Additionally, our results lend support to a FOMO mechanism while they are not suggestive of a mechanism by which negative content is the channel through which social media generates feelings of social isolations. Overall, our findings suggest that institutional context may not play an important role in the social media - social isolation relationship."
keywords: [Social Isolation, Social Media, Digital Communication, China]
format:
  tandf-pdf:
    keep-tex: true 
execute: 
  echo: false
  warning: false
keep-tex: true
bibliography: references.bib
csl: taylor-and-francis-apa.csl
---

### 2023-10-08 tandf/Social-Isolation-in-China.tex
File cleanup

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Lonely and online: an investigation of social media use and social isolation in China},
  pdfauthor={Jason Gainous; Andrew W. MacDonald},
  pdfkeywords={Social Isolation, Social Media, Digital
Communication, China},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\author{\name{Jason Gainous\textsuperscript{a} and Andrew W.
MacDonald\textsuperscript{b}\thanks{CONTACT Andrew W.
MacDonald. Email: andrew.macdonald@dukekunshan.edu.cn}}
\affil{\textsuperscript{a}Department of Mass Communication, University
of Sharjah, Sharjah, United Arab Emirates;
\textsuperscript{b}Division of Social Sciences, Duke Kunshan
University, Kunshan, China}}

%\author[1]{Jason Gainous%
%%
%}
% \ead{jgainous@sharjah.ac.ae} 
%\author[2]{Andrew W. MacDonald%
%\corref{cor1}%
%}
% \ead{andrew.macdonald@dukekunshan.edu.cn} 
%

@@

\begin{keywords}
    Social Isolation, Social Media, Digital Communication, 
    China
\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, sharp corners, boxrule=0pt, frame hidden, enhanced, breakable, interior hidden]}{\end{tcolorbox}}\fi

>>>>

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Lonely and online: an investigation of social media use and social isolation in China},
  pdfkeywords={Social Isolation, Social Media, Digital
Communication, China},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

%

@@

\begin{keywords}
    Social Isolation, Social Media, Digital Communication, 
    China
\end{keywords}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, interior hidden, sharp corners, frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
